---
title: "Analizing trends in Canadian glacier mass"
author: "Eugene Oldman"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The data used in study is taken from <http://open.canada.ca/en/open-data>[^1].

[^1]: Here is the [direct link](http://www20.statcan.gc.ca/tables-tableaux/cansim/csv/01530102-eng.zip)
to data download.

```{r, echo = F}
glacier <- read.csv("glacier.csv", comment.char = "#", na.strings = "..")
```

The data set contains `r nrow(glacier)` measurements of `r nlevels(glacier$GEO)` 
Canadian glacier mass balans, collected from `r min(glacier$Ref_Date)` till 
`r max(glacier$Ref_Date)`. Namely, the file includes these glaciers:

```{r, echo = F}
levels(glacier$GEO)
```

## Hypothesis

We are interested in finding out whether there is statistically
signification change in mass balance over the observed time period. For this 
purpose we use **R** (version `r getRversion()`) and an appropriate 
statistical test clled _t-test_: $$ t = \frac{\overline{x} - \mu_0}{s/\sqrt{n}}.$$

The workflow is as follows:

1. Read file file
2. Run t-test for each glacier and collect p-values
3. Support the evidence with 
    + a table of result;
    + a plot than coulde help demonstrate the effect.
    

