---
title: "Analizing trends in Canadian glacier mass"
author: "Eugene Oldman"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    keep_tex: yes
    toc: yes
params:
  filename: glacier.csv
bibliography: bibl.bib
urlcolor: blue
---

```{r setup, include=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
options(scipen = 0, digits = 3)
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F)
```

## Introduction

The data used in study is taken from <http://open.canada.ca/en/open-data>[^1]. The
algorithm is taken from @AntonovErmakov_RandsmCubaturesQMC.

[^1]: Here is the [direct link](http://www20.statcan.gc.ca/tables-tableaux/cansim/csv/01530102-eng.zip)
to data download.

```{r}
glacier <- read.csv(params$filename, comment.char = "#", na.strings = "..")
```

The data set contains `r nrow(glacier)` measurements of `r nlevels(glacier$GEO)` 
Canadian glacier mass balans, collected from `r min(glacier$Ref_Date)` till 
`r max(glacier$Ref_Date)`. Namely, the file includes these glaciers:

```{r}
levels(glacier$GEO)
```

## Hypothesis

We are interested in finding out whether there is statistically
signification change in mass balance over the observed time period. For this 
purpose we use **R** (version `r getRversion()`) and an appropriate 
statistical test clled _t-test_: $$ t = \frac{\overline{x} - \mu_0}{s/\sqrt{n}}.$$

The workflow is as follows:

1. Read file file
2. Run t-test for each glacier and collect p-values
3. Support the evidence with 
    + a table of result;
    + a plot than could help demonstrate the effect.

## Analysis

```{r analysis, cache = T}
glacier <- glacier %>% 
  select(Ref_Date, GEO, MEASURE, Value) %>% 
  filter(MEASURE == "Annual mass balance") %>% 
  separate(GEO, c("Name", "Location"), sep = " - ")

# descriptive analysis
g1 <- glacier %>% 
  group_by(Name) %>% 
  summarise(YearsObserved = n(),
             MeanChange = mean(Value, na.rm = T),
             WorstChange = min(Value, na.rm = T),
             WorstYear = Ref_Date[which.min(Value)])
# t-test
g2 <- glacier %>% 
  group_by(Name) %>% 
  do({
    tt <- t.test(.$Value, alternative = "less", mu = 0, conf.level = 0.99)
    data.frame(PValue = tt$p.value,
               ConfidenceLimit = tt$conf.int[2])
  })

left_join(g1, g2, by = "Name") %>% 
  knitr::kable(caption = "Descriptive statistics and confidence intervals",
               digits = c(0, 0, 2, 0, 0, 10, 2))  # точность чисел в столбцах
```

    
```{r ggplot, fig.width = 10}
ggplot(glacier, aes(Ref_Date, Value)) + 
  geom_line() +
  geom_hline(data = g1, aes(yintercept = MeanChange),
             color = "red", linetype = "dashed", alpha = 0.8) +
  facet_wrap(~Name, nrow = 2)
```

## Bibliograpfy
